Compiling refinement types to dependent types

### 2020-07-25 tex/paper.tex
Define the translation for TWF-ADT
More consistent \nonterm G usage

    We resort to \textsc{CT-Form} on the right.
    This is well-formed,
    since $\Tranty(\nonterm G \vdash \nonterm{ts}_1)$ produces a derivation of $\nonterm{GC} \vdash \nonterm{tc}_1 : \star$,
    and similarly we get a derivation of $\nonterm{GC}, \gterm x : \nonterm{tc}_1 \vdash \nonterm{tc}_2 : \star$ from
    the other invocation of $\Tranty$.
  \item \textsc{TWF-ADT}.
    \todo[inline]{Don't forget to define this.}
\end{itemize}

@@

  \item \textsc{T-Var}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\
                   \gterm x : \nonterm{ts} \in \nonterm G}
                  {\nonterm G \vdash \gterm x : \nonterm{ts}}
          \longmapsto
        \inferrule{x : \nonterm{tc} \in \nonterm{GC}}
                  {\nonterm{GC} \vdash \gterm x : \nonterm{tc}},    \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),       \\
                   &\nonterm{tc} = \tranty(\Gamma \vdash \nonterm{ts}).
    \end{align*}

@@

    By definition of $\Tranctx$,
    if $\nonterm G$ contains a binding for the name $x$,
    then $\nonterm{GC}$ also contains a binding for that name,
    and its type is precisely $\tranty(\Gamma \vdash \nonterm{ts})$.
    Thus, we are allowed to use the (derived) core typing rule \textsc{CT-VarW}.
\end{itemize}

>>>>

    We resort to \textsc{CT-Form} on the right.
    This is well-formed,
    since $\Tranty(\nonterm G \vdash \nonterm{ts}_1)$ produces a derivation of $\nonterm{GC} \vdash \nonterm{tc}_1 : \star$,
    and similarly we get a derivation of $\nonterm{GC}, \gterm x : \nonterm{tc}_1 \vdash \nonterm{tc}_2 : \star$ from
    the other invocation of $\Tranty$.
  \item \textsc{TWF-ADT}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\\\
                   \overline{\nonterm G \vdash \nonterm{ts}_i}^i
                  }
                  {\nonterm G \vdash \langle \overline{l_i : \nonterm{ts}_i}^i \rangle}
          \longmapsto
        \inferrule{\overline{\Tranty(\nonterm G \vdash \nonterm{ts}_i)}^i}
                  {\nonterm{GC} \vdash \langle \overline{l_i : \nonterm{tc}_i}^i \rangle : \star}, \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),                                         \\
                   &\nonterm{tc}_i = \tranty(\nonterm G \vdash \nonterm{ts}_i).
    \end{align*}

    It can be seen that the right-hand side is well-defined
    by an argument similar to ones for the previous clauses.
\end{itemize}

@@

  \item \textsc{T-Var}.
    \begin{align*}
      & \inferrule{\nonterm G \ctxok \\
                   \gterm x : \nonterm{ts} \in \nonterm G}
                  {\nonterm G \vdash \gterm x : \nonterm{ts}}
          \longmapsto
        \inferrule{x : \nonterm{tc} \in \nonterm{GC}}
                  {\nonterm{GC} \vdash \gterm x : \nonterm{tc}},    \\
      \text{where}~&\nonterm{GC} = \Tranctx(\nonterm G \ctxok),       \\
                   &\nonterm{tc} = \tranty(\nonterm G \vdash \nonterm{ts}).
    \end{align*}

@@

    By definition of $\Tranctx$,
    if $\nonterm G$ contains a binding for the name $x$,
    then $\nonterm{GC}$ also contains a binding for that name,
    and its type is precisely $\tranty(\nonterm G \vdash \nonterm{ts})$.
    Thus, we are allowed to use the (derived) core typing rule \textsc{CT-VarW}.
\end{itemize}
